\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[
	letterpaper,
	margin=0.6in,
	top=0.5in,
	bottom=0.5in,
]{geometry}
\usepackage{enumitem}

% Remove indentations at beginning of lines
\setlength{\parindent}{0pt}
% Remove header & footer (i.e. page number)
\thispagestyle{empty}
% Define title layout
\renewcommand{\maketitle}{
	\begin{center}
	{\huge\bfseries\theauthor}

	\vspace{0.5em}
	david@qiu.dev -- https://qiu.dev -- 253-525-7070 -- github.com/diracs-delta
	\end{center}
}
% Define format and spacing of section headers
\titleformat{\section}{\huge\bfseries\lowercase}{}{-1em}{}[\titlerule]
\titleformat{\subsection}{\bfseries\large}{$\hspace{0em}$}{0em}{}
\titleformat{\subsubsection}{\bfseries}{}{1em}{}
\titlespacing\section{0pt}{0pt}{4pt}
\titlespacing\subsection{0pt}{3pt}{1pt}
\titlespacing\subsubsection{0pt}{3pt}{0pt}
% Define TM macro
\newcommand{\TM}{\texttrademark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\author{David Qiu}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Objective}
To build fast, reliable, and scalable fullstack software developed with the
latest technologies and SaaS platforms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\subsection{University of Illinois at Urbana-Champaign \hfill May 2020}
B.S.\ in Chemistry with Highest Distinction; James Scholar, Dean's List, Cum Laude (GPA: 3.92)

\subsubsection{Relevant Coursework}

\begin{itemize}[noitemsep,nolistsep]
	\item Phys.\ Chem.\ I--II; Inorg.\ Chem.; Org.\ Chem.\ I--II; Instrumental
		Char.; Quant.\ Anal.

	\item Lin.\ Alg.; Diff.\ Eq.; Calc.\ I--III; Univ.\ C.\ Mech., E+M, Q.\
		Mech.; Num.\ Anal.
\end{itemize}

\subsection{duPont Manual High School \hfill May 2018}
Valedictorian, National Merit Finalist. SAT 1570/1600, ACT 35/36.

% \begin{itemize}[noitemsep,nolistsep]
% 	\item Placed 2nd in Undergraduate Neuroscience Convention at the University
% 		of Louisville.\hfill\textbf{Apr.\ 2016}
% \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research + Employment}

Techstack and full CV viewable at https://qiu.dev/techstack.

\subsection{Fullstack Developer, Helium Development LLC \hfill Feb.\ 2021 -- *}
\begin{itemize}[noitemsep,nolistsep]
	\item Learned Typescript, React, and Rails in 2 weeks beforehand. Began
		delivering value on day 1.

	\item Utilized Scrum methodology to deliver iterative improvements on the
		monolithic codebase of Helium's flagship product, \emph{Customer Fields},
		a Shopify app that allows merchants to collect, store, and analyze
		customer data.

		\begin{itemize}[noitemsep,nolistsep]
			\item Advocated and enforced best practices to improve code quality
				and maintainability; Implemented a suite of unit tests,
				refactored bloated React components, introduced the latest
				development tooling, and collaborated with UI designer and
				project manager to deliver fantastic user experiences.
		\end{itemize}

	\item Exclusively entrusted with the development of the admin interface to
		our latest app in a joint collaboration with Snapbar, \emph{Holar}, a
		SaaS product that enables event coordinators to collect, store, and
		distribute portrait photos of employees and customers.

	\item Developed a CI pipeline script integrated with the Netlify build
		process, which uploads compiled GraphQL serverless functions to the
		Google cloud platform on each branch push.
\end{itemize}

\subsection{Researcher and TA, University of Illinois at U-C
            \hfill Nov.\ 2018 -- May 2021}
\begin{itemize}[noitemsep,nolistsep]
	\item \textbf{Hirata Group, 2019--2021}: Contributed to development of a
		novel stochastic technique in the evaluation of higher-order
		perturbation energies for very large molecular systems, termed
		\emph{Monte Carlo perturbation theory}. Parsed, processed, and
		interpreted large numerical datasets via numpy and pandas. Run on the
		Blue Waters supercomputer at the NCSA.

	\item \textbf{TA for Phys.\ Chem.\ I, Spr.\ 2020}: Taught an
		introductory course in quantum mechanics to 60+
		juniors and seniors under Professor Hirata.

	\item \textbf{Jain Group, 2018--2019}: Performed electronic impedance
		spectroscopy to characterize the superionic properties of twin-domain
		Cu$_2$S nanocrystals, a potential solid-state electrolyte for
		next-generation lithium-ion batteries.
\end{itemize}

% \subsection{Medical Scribe, OSF Heart of Mary Medical Center ED \hfill May.\ 2019 -- Jun.\ 2020}
% \begin{itemize}[noitemsep, nolistsep]
% 	\item Documented medical charts for ED physicians using the Epic EMR
% 		system. Embraced learning the fundamentals of medicine in a
% 		stressful, hectic environment while building friendships with
% 		numerous ED physicians.
% \end{itemize}

\section{Involvement and Honors}
\begin{itemize}[noitemsep,nolistsep]
	\item 2020 ACS Undergraduate Award in Physical Chemistry, Worth H.\ Rodebush Award
	\hfill\textbf{May 2020}

	\item Academic Chair of American Chemical Society, UIUC Chapter.
	\hfill\textbf{May 2019 -- May 2020}

	\item Oliver J.\ Bell Merit Scholar, Homer J.\ and Edith M.\ Birch
	Scholar.
	\hfill\textbf{Aug. 2019}

	\item 2019 John E.\ Gieseking Scholar (for undergraduate research).
	\hfill\textbf{May 2019}

	\item Named ACS High Honors (Top 50 in the U.S.\ Chemistry Olympiad).
	\hfill\textbf{May 2018}
\end{itemize}

\section{Selected Publications}

\begin{itemize}[noitemsep, nolistsep]
	\item Qiu, David.\ \emph{Investigations into Molecular Dimers via
		Many-body Monte Carlo Methods.}\ Undergraduate thesis.\ 2020.

	\item Doran, Alexander; Qiu, David; Hirata, So. \emph{Monte Carlo MP2-F12
		for noncovalent interactions: The C60 dimer.} To be published. 2021.
\end{itemize}

% Create footnote without a corresponding marker.
% See: https://tex.stackexchange.com/questions/30720/footnote-without-a-marker
\newcommand\blfootnote[1]{%
	\begingroup
	\renewcommand\thefootnote{}\footnote{#1}%
	\addtocounter{footnote}{-1}%
	\endgroup
}

\blfootnote{Note: * denotes present or expected in the near future.}
\blfootnote{Last updated 13 June 2021.}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

